article title

### 2022-07-19 article.tex
Convert Greek mathematics to table

\subsection{Greek unicode}
\label{sec:greek_unicode}

@@

\begin{table}[H]
\begin{flushleft}
\begin{tabular}{lcccc}
\toprule
letter & code & miniscule & code & majuscule \\
\midrule
alpha   & 03b1 & α & 0391 & Α \\
beta    & 03b2 & β & 0392 & Β \\
gamma   & 03b3 & γ & 0393 & Γ \\
delta   & 03b4 & δ & 0394 & Δ \\
epsilon & 03b5 & ε & 0395 & Ε \\
zeta    & 03b6 & ζ & 0396 & Ζ \\
eta     & 03b7 & η & 0397 & Η \\
theta   & 03b8 & θ & 0398 & Θ \\
iota    & 03b9 & ι & 0399 & Ι \\
kappa   & 03b1 & α & 039a & Κ \\
lambda  & 03bb & λ & 039b & Λ \\
mu      & 03bc & μ & 039c & Μ \\
nu      & 03bd & ν & 039d & Ν \\
xi      & 03be & ξ & 039e & Ξ \\
omicron &      & o &      & O \\
pi      & 03c0 & π & 03ao & Π \\
rho     & 03c1 & ρ & 03a1 & Ρ \\
sigma   & 03c3 & σ & 03a3 & Σ \\
tau     & 03c4 & τ & 03a4 & Τ \\
upsilon & 03c5 & υ & 03a5 & Υ \\
phi     & 03c6 & φ & 03a6 & Φ \\
chi     & 03c7 & χ & 03a7 & Χ \\
psi     & 03c8 & ψ & 03a8 & Ψ \\
omega   & 03c9 & ω & 03a9 & Ω \\
\bottomrule
\end{tabular}
\end{flushleft}
\end{table}

@@

alpha $\alpha$ A \\
beta $\beta$ B \\
gamma $\gamma$ $\Gamma$ \\
delta $\delta$ $\Delta$ \\
epsilon$\epsilon$ E \\
zeta $\zeta$ Z \\
eta $\eta$ H\\
theta $\theta$ $\Theta$ \\
iota $\iota$ I \\
kappa $\kappa$ K \\
lambda $\lambda$ $\Lambda$ \\
mu $\mu$ M \\
nu $\nu$ N \\
xi $\xi$ $\Xi$ \\
omicron o O \\
pi $\pi$ $\Pi$\\
rho $\rho$ P \\
sgima $\sigma$ $\Sigma$ \\
tau $\tau$ T \\
upsilon $\upsilon$ $\Upsilon$ \\
phi $\phi$ $\Phi$ \\
chi $\chi$ X \\
psi $\psi$ $\Psi$ \\
omega $\omega$ $\Omega$ \\

>>>>

\subsection{Greek Unicode}
\label{sec:greek_unicode}

@@

\begin{table}[H]
\begin{flushleft}
\begin{tabular}{lcccc}
\toprule
letter & code & miniscule & code & majuscule \\
\midrule
alpha   & 03b1 & α & 0391 & Α \\
beta    & 03b2 & β & 0392 & Β \\
gamma   & 03b3 & γ & 0393 & Γ \\
delta   & 03b4 & δ & 0394 & Δ \\
epsilon & 03b5 & ε & 0395 & Ε \\
zeta    & 03b6 & ζ & 0396 & Ζ \\
eta     & 03b7 & η & 0397 & Η \\
theta   & 03b8 & θ & 0398 & Θ \\
iota    & 03b9 & ι & 0399 & Ι \\
kappa   & 03b1 & α & 039a & Κ \\
lambda  & 03bb & λ & 039b & Λ \\
mu      & 03bc & μ & 039c & Μ \\
nu      & 03bd & ν & 039d & Ν \\
xi      & 03be & ξ & 039e & Ξ \\
omicron &      & o &      & O \\
pi      & 03c0 & π & 03ao & Π \\
rho     & 03c1 & ρ & 03a1 & Ρ \\
sigma   & 03c3 & σ & 03a3 & Σ \\
tau     & 03c4 & τ & 03a4 & Τ \\
upsilon & 03c5 & υ & 03a5 & Υ \\
phi     & 03c6 & φ & 03a6 & Φ \\
chi     & 03c7 & χ & 03a7 & Χ \\
psi     & 03c8 & ψ & 03a8 & Ψ \\
omega   & 03c9 & ω & 03a9 & Ω \\
\bottomrule
\end{tabular}
\label{tab:greek_unicode}
\caption{Greek Unicode}
\end{flushleft}
\end{table}

@@

Greek letters can be inserted in mathematics. These are naturally italicized.

\begin{table}[H]
\begin{flushleft}
\begin{tabular}{lcccc}
\toprule
letter & code & miniscule & code & majuscule \\
\midrule
alpha   & \$\textbackslash alpha\$   & $\alpha$   & \$A\$                      & $A$ \\
beta    & \$\textbackslash beta\$    & $\beta$    & \$B\$                      & $B$ \\
gamma   & \$\textbackslash gamma\$   & $\gamma$   & \$\textbackslash Gamma\$   & $\Gamma$ \\
delta   & \$\textbackslash delta\$   & $\delta$   & \$\textbackslash Delta\$   & $\Delta$ \\
epsilon & \$\textbackslash epsilon\$ & $\epsilon$ & \$E\$                      & $E$ \\
zeta    & \$\textbackslash zeta\$    & $\zeta$    & \$Z\$                      & $Z$ \\
eta     & \$\textbackslash eta\$     & $\eta$     & \$H\$                      & $H$ \\
theta   & \$\textbackslash theta\$   & $\theta$   & \$\textbackslash Theta\$   & $\Theta$ \\
iota    & \$\textbackslash iota\$    & $\iota$    & \$I\$                      & $I$ \\
kappa   & \$\textbackslash kappa\$   & $\kappa$   & \$K\$                      & $K$ \\
lambda  & \$\textbackslash lambda\$  & $\lambda$  & \$\textbackslash Lambda\$  & $\Lambda$ \\
mu      & \$\textbackslash mu\$      & $\mu$      & \$M\$                      & $M$ \\
nu      & \$\textbackslash nu\$      & $\nu$      & \$N\$                      & $N$ \\
xi      & \$\textbackslash xi\$      & $\xi$      & \$\textbackslash Xi\$      & $\Xi$ \\
omicron & \$o\$                      & $o$        & \$O\$                      & $O$ \\
pi      & \$\textbackslash pi\$      & $\pi$      & \$\textbackslash Pi\$      & $\Pi$ \\
rho     & \$\textbackslash rho\$     & $\rho$     & \$P\$                      & $P$ \\
sigma   & \$\textbackslash sigma\$   & $\sigma$   & \$\textbackslash Sigma\$   & $\Sigma$ \\
tau     & \$\textbackslash tau\$     & $\tau$     & \$T\$                      & $T$ \\
upsilon & \$\textbackslash upsilon\$ & $\upsilon$ & \$\textbackslash Upsilon\$ & $\Upsilon$ \\
phi     & \$\textbackslash phi\$     & $\phi$     & \$\textbackslash Phi\$     & $\Phi$ \\
chi     & \$\textbackslash chi\$     & $\chi$     & \$X\$                      & $X$ \\
psi     & \$\textbackslash psi\$     & $\psi$     & \$\textbackslash Psi\$     & $\Psi$ \\
omega   & \$\textbackslash omega\$   & $\omega$   & \$\textbackslash Omega\$   & $\Omega$ \\
\bottomrule
\end{tabular}
\label{tab:greek_mathematics}
\caption{Greek mathematics}
\end{flushleft}
\end{table}
